---
title: "Untitled"
author: "kat"
date: "2/10/2022"
output:
  html_document:
    code_folding: hide
    theme: yeti
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

## Preliminary stuff

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(lme4)
library(readxl)
library(extrafont)
library(sysfonts)
library(irr)
library(lavaan)
library(lavaanPlot)
library(DiagrammeRsvg)

font_add_google("Source Sans Pro")

dat <- read_excel("dissertation - anon.xlsx")
```


## Overall Analyses {.tabset}

### Overall, Inclusive, no slope
```{r}
overall_inclusive <- glmer(inclusive ~ questiontype * fragcode + (1|experimenter), dat, binomial)
summary(overall_inclusive)
```


### Overall, Inclusive, with slope
```{r}
overall_inclusive_slope <- glmer(inclusive ~ questiontype * fragcode + (1 + questiontype | experimenter), dat, binomial)
summary(overall_inclusive_slope)
```


### Inclusive Model Comparison
```{r}
anova(overall_inclusive, overall_inclusive_slope)
```


### Reliability 

#### Splithalf - Overall, All Data
```{r}
overall_sh1_noprep <- dat %>%
  select(experimenter, round, questiontype, inclusive, splithalf) %>%
  filter(splithalf == 1 & questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

overall_sh1_prep <- dat %>%
  select(experimenter, round, questiontype, inclusive, splithalf) %>%
  filter(splithalf == 1 & questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

overall_sh2_noprep <- dat %>%
  select(experimenter, round, questiontype, inclusive, splithalf) %>%
  filter(splithalf == 2 & questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

overall_sh2_prep <- dat %>%
  select(experimenter, round, questiontype, inclusive, splithalf) %>%
  filter(splithalf == 2 & questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

overall_sh1_difference <- overall_sh1_prep$meanresponse - overall_sh1_noprep$meanresponse

overall_sh2_difference <- overall_sh2_prep$meanresponse - overall_sh2_noprep$meanresponse


cor.test(overall_sh1_difference, overall_sh2_difference)
```


#### ICC for Splithalf - Overall, All Data
```{r}
#make the two priming effects kith
overall_prime_sh1 <- as.data.frame(overall_sh1_difference)
overall_prime_sh2 <- as.data.frame(overall_sh2_difference)

overall_primes_sh <- cbind(overall_prime_sh1, overall_prime_sh2)

icc(overall_primes_sh, model = "twoway", type = "agreement", unit = "single")
```


#### Test-Retest - Overall, All Data
```{r}
overall_round1_reliability_noprep <- dat %>%
  filter(round == 1) %>%
  select(experimenter, round, questiontype, inclusive, term) %>%
  filter(questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

overall_round1_reliability_prep <- dat %>%
  filter(round == 1) %>%
  select(experimenter, round, questiontype, inclusive, term) %>%
  filter(questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

overall_round2_reliability_noprep <- dat %>%
  filter(round == 2) %>%
  select(experimenter, round, questiontype, inclusive, term) %>%
  filter(questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

overall_round2_reliability_prep <- dat %>%
  filter(round == 2) %>%
  select(experimenter, round, questiontype, inclusive, term) %>%
  filter(questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))


overall_round1_difference <- overall_round1_reliability_prep$meanresponse - overall_round1_reliability_noprep$meanresponse

overall_round2_difference <- overall_round2_reliability_prep$meanresponse - overall_round2_reliability_noprep$meanresponse

cor.test(overall_round1_difference, overall_round2_difference)
```


#### ICC for Test-Retest - Overall, All Data
```{r}
overall_prime_round1 <- as.data.frame(overall_round1_difference)
overall_prime_round2 <- as.data.frame(overall_round2_difference)

overall_prime_rounds <- cbind(overall_prime_round1, overall_prime_round2)

icc(overall_prime_rounds, model = "twoway", type = "agreement", unit = "single")
```
### Global Priming Effect

```{r}
incl_exp <- dat %>%
  group_by(experimenter, questiontype)%>%
  mutate(incl_mean = mean(inclusive, na.rm = TRUE))

p <- ggplot(incl_exp, aes(incl_mean, questiontype,fill = questiontype, alpha = 0.9)) + 
   geom_boxplot() + 
  #scale_fill_manual(values = c("#418D87", "#73224E")) + 
   theme_classic() + 
   theme( 
   axis.title.x = element_text(family = "Source Sans Pro"),
   axis.text.x = element_text(family = "Source Sans Pro"), 
   axis.title.y = element_text(family = "Source Sans Pro"), 
   axis.text.y = element_text(family = "Source Sans Pro"), 
   legend.position = "none",
   plot.title = element_text(hjust = 0.5)
   ) + 
   scale_y_discrete(labels = c("Non-Prep", "Prep"))

p1 <- p + labs(title = "Responses by Question Type",
                x = "Proportion of Prepositional Responses", 
                y = "Question Type"
               ) +
  scale_fill_grey()
p1

ggsave("overall_plot.jpeg", plot = p1)
```


### Priming Effect by Experimenter Plots

Plot 1
```{r}
overall_prime_noprep_p1 <- dat %>%
  select(experimenter, round, questiontype, inclusive, splithalf) %>%
  filter(questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse_noprep = mean(inclusive, na.rm = TRUE))

overall_prime_prep_p1 <- dat %>%
  select(experimenter, round, questiontype, inclusive, splithalf) %>%
  filter(questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse_prep = mean(inclusive, na.rm = TRUE))

line <- merge(overall_prime_noprep_p1, overall_prime_prep_p1, by = "experimenter")

# make long
line_long <- gather(line, condition, mean, meanresponse_noprep:meanresponse_prep, factor_key = TRUE)

#rename reponse variables
line_long$condition <- recode_factor(line_long$condition, meanresponse_noprep  = "noprep",
                                     meanresponse_prep = "prep")

line_long$experimenter <- as.factor(line_long$experimenter)

#make those labels purdy
plot_labels <- c("No Preposition", "Preposition")

by_exp_plot <- ggplot(line_long, aes(condition, mean, group = experimenter, color = experimenter)) +
  geom_line() +
  theme_classic() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5),
  ) +
  labs(title = "Proportion of Priming Elicited by Experimenter per Condition", x = "Condition", y = "Proportion of Prepositional Responses Elicited") +
  scale_x_discrete(labels = plot_labels)

ggsave("by_exp_plot.jpeg", plot = by_exp_plot)
```

Plot 2
```{r}
overall_prime_noprep_p2 <- dat %>%
  select(experimenter, round, questiontype, inclusive, splithalf) %>%
  filter(questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

overall_prime_prep_p2 <- dat %>%
  select(experimenter, round, questiontype, inclusive, splithalf) %>%
  filter(questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

overall_prime_effect <- overall_prime_noprep_p2$meanresponse - overall_prime_prep_p2$meanresponse

overall_prime <- data.frame(overall_prime_effect) %>% arrange(overall_prime_effect)

overall_prime$row_num <- seq.int(nrow(overall_prime))


priming_effect <- ggplot() + 
  geom_point(data = overall_prime, mapping = aes(x = row_num, y = overall_prime_effect), size = 3, shape = 21, fill = "white") +
  theme(legend.position ="right") + 
  labs(x = "Experimenters", y = "Priming Effect", title="Priming Effect by Experimenter") +
  theme_bw() +
  theme(
    panel.border = element_blank(),
    panel.grid.minor = element_blank(), 
    panel.grid.major = element_blank(),
    axis.line = element_line(colour = "black"),
    axis.title.x = element_text(color = "black", size = 12), 
    axis.title.y = element_text(color = "black", size = 12), 
    axis.text.x = element_text(color = "black", size = 9), 
    axis.text.y = element_text(color = "black", size = 12), 
    legend.text = element_text(color = "black", size = 12), 
    plot.title = element_text(color = "black", size = 12, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
    )

ggsave("primingeffect.jpeg", plot=priming_effect, width = 6, height = 4)
```

```{r}

sh1_noprep <- dat %>% 
  select(experimenter, questiontype, inclusive, splithalf) %>%
  filter(splithalf == 1, questiontype == 'noprep') %>%
  group_by(experimenter) %>%
   summarise(meanresponse = mean(inclusive, na.rm=TRUE))

sh1_prep <- dat %>% 
  select(experimenter, questiontype, inclusive, splithalf) %>%
  filter(splithalf == 1, questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

sh2_noprep <- dat %>% 
  select(experimenter, questiontype, inclusive, splithalf) %>%
  filter(splithalf == 2, questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

sh2_prep <- dat %>% 
  select(experimenter, questiontype, inclusive, splithalf) %>%
  filter(splithalf == 2, questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

sh1_difference <- sh1_prep$meanresponse - sh1_noprep$meanresponse

sh2_difference <- sh2_prep$meanresponse - sh2_noprep$meanresponse

cor.test(sh1_difference, sh2_difference)

sh_scatter <- data.frame(sh1_difference, sh2_difference)

splithalfplot <- ggplot(test_scatter, aes(sh1_difference, sh2_difference)) +
  geom_point(size = 2) +
  labs(title = "Split-Half Reliablity", x = "Split-Half 1 Priming Effect", y = "Split-Half 2 Priming Effect") +
  ylim(-0.1, 0.3) +
  xlim(-0.1, 0.3) +
  theme(
    axis.line = element_line(colour = "black"),
    axis.title.x = element_text(color = "black", size = 12), 
    axis.title.y = element_text(color = "black", size = 12),
    axis.text.x = element_text(color = "black", size = 12), 
    axis.text.y = element_text(color = "black", size = 12),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    plot.title = element_text(color = "black", size = 12, face = "bold", hjust = 0.5)
  )

ggsave("splithalfplot.jpeg", plot=splithalfplot, width = 6, height = 4)
```


# Plot correlation for test-retest
```{r}
r1_noprep <- dat %>% 
  select(experimenter, round, questiontype, inclusive) %>%
  filter(round == 1, questiontype == 'noprep') %>%
  group_by(experimenter) %>%
   summarise(meanresponse = mean(inclusive, na.rm=TRUE))

r1_prep <- dat %>% 
  select(experimenter, round, questiontype, inclusive) %>%
  filter(round == 1, questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm=TRUE))

r2_noprep <- dat %>% 
  select(experimenter, round, questiontype, inclusive) %>%
  filter(round == 2, questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm=TRUE))

r2_prep <- dat %>% 
  select(experimenter, round, questiontype, inclusive) %>%
  filter(round == 2, questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm=TRUE))

r1_difference <- r1_prep$meanresponse - r1_noprep$meanresponse

r2_difference <- r2_prep$meanresponse - r2_noprep$meanresponse

test_rounds <- data.frame(r1_difference, r2_difference)

test_retest <- ggplot(test_rounds, aes(r1_difference, r2_difference)) +
  geom_point(color = "black", size = 2) +
  labs(x = "Round 1 Difference", y = "Round 2 Difference", title = "Test-Retest Reliability") +
  xlim(-0.1, 0.3) +
  theme(
    axis.line = element_line(colour = "black"),
    axis.title.x = element_text(color="black", size = 12, family = "Source Sans Pro"), 
    axis.title.y = element_text(color="black", size = 12, family = "Source Sans Pro"),
    axis.text.x = element_text(color="black", size = 12, family = "Source Sans Pro"), 
    axis.text.y = element_text(color="black", size = 12, family = "Source Sans Pro"),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    plot.title = element_text(hjust = 0.5)
  )

ggsave("testretest.jpeg", plot = test_retest, width = 6, height = 4)
```

## By Experiment {.tabset}

### Experiment 1 (Spring 2021)

#### Overall, Inclusive, no slope
```{r}
exp1 <- dat %>%
  filter(term == 'sp_21')

exp1_overall_inclusive <- glmer(inclusive ~ questiontype * fragcode + (1 | experimenter), exp1, binomial)
summary(exp1_overall_inclusive)
```


#### Overall, Inclusive, with slope
```{r}
exp1_overall_inclusive_slope <- glmer(inclusive ~ questiontype * fragcode + (1 + questiontype | experimenter), exp1, binomial)
summary(exp1_overall_inclusive_slope)
```


#### Model Comparison
```{r}
anova(exp1_overall_inclusive, exp1_overall_inclusive_slope)
```


#### Splithalf - Experiment 1
```{r}
exp1_sh1_noprep <- dat %>%
  filter(term == 'sp_21') %>%
  select(experimenter, questiontype, inclusive, splithalf) %>%
  filter(splithalf == 1, questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

exp1_sh1_prep <- dat %>%
  filter(term == 'sp_21') %>%
  select(experimenter, questiontype, inclusive, splithalf) %>%
  filter(splithalf == 1, questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

exp1_sh2_noprep <- dat %>%
  filter(term == 'sp_21') %>%
  select(experimenter, questiontype, inclusive, splithalf) %>%
  filter(splithalf == 2, questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

exp1_sh2_prep <- dat %>%
  filter(term == 'sp_21') %>%
  select(experimenter, questiontype, inclusive, splithalf) %>%
  filter(splithalf == 2, questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))


exp1_sh1_difference <- exp1_sh1_prep$meanresponse - exp1_sh1_noprep$meanresponse

exp1_sh2_difference <- exp1_sh2_prep$meanresponse - exp1_sh2_noprep$meanresponse

cor.test(exp1_sh1_difference, exp1_sh2_difference)
```


#### ICC for Splithalf - Experiment 1
```{r}
#make the two priming effects kith
exp1_prime_sh1 <- as.data.frame(exp1_sh1_difference)
exp1_prime_sh2 <- as.data.frame(exp1_sh2_difference)

exp1_primes_sh <- cbind(exp1_prime_sh1, exp1_prime_sh2)

icc(exp1_primes_sh, model = "twoway", type = "agreement", unit = "single")
```


#### Test-Retest - Experiment 1
```{r}
exp1_round1_reliability_noprep <- dat %>%
  filter(round == 1 & term == "sp_21") %>%
  select(experimenter, round, questiontype, inclusive, term) %>%
  filter(questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

exp1_round1_reliability_prep <- dat %>%
  filter(round == 1 & term == "sp_21") %>%
  select(experimenter, round, questiontype, inclusive, term) %>%
  filter(questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

exp1_round2_reliability_noprep <- dat %>%
  filter(round == 2 & term == "sp_21") %>%
  select(experimenter, round, questiontype, inclusive, term) %>%
  filter(questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

exp1_round2_reliability_prep <- dat %>%
  filter(round == 2 & term == "sp_21") %>%
  select(experimenter, round, questiontype, inclusive, term) %>%
  filter(questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

exp1_round1_difference <- exp1_round1_reliability_prep$meanresponse - exp1_round1_reliability_noprep$meanresponse

exp1_round2_difference <- exp1_round2_reliability_prep$meanresponse - exp1_round2_reliability_noprep$meanresponse

cor.test(exp1_round1_difference, exp1_round2_difference)
```


#### ICC for Test-Retest - Experiment 1
```{r}
exp2_prime_round1 <- as.data.frame(exp1_round1_difference)
exp2_prime_round2 <- as.data.frame(exp1_round2_difference)

exp2_prime_rounds <- cbind(exp2_prime_round1, exp2_prime_round2)

icc(exp2_prime_rounds, model = "twoway", type = "agreement", unit = "single")
```


### Experiment 2 (Summer 2021, Fall 2021) 

#### Overall, Inclusive, no slope
```{r}
# subset first
exp2 <- dat %>%
  filter(term == 'su_21' | term == "fa_21")

exp2_overall_inclusive <- glmer(inclusive ~ questiontype * fragcode + (1 | experimenter), exp2, binomial)

summary(exp2_overall_inclusive)
```


#### Overall, Inclusive with slope
```{r}
exp2_overall_inclusive_slope <- glmer(inclusive ~ questiontype * fragcode + (1 + questiontype | experimenter), exp2, binomial)

summary(exp2_overall_inclusive_slope)
```


#### Model Comparison
```{r}
anova(exp2_overall_inclusive, exp2_overall_inclusive_slope)
```


#### Splithalf - Experiment 2
```{r}
exp2_sh1_noprep <- dat %>%
  filter(term == 'su_21' | term == 'fa_21') %>%
  select(experimenter, splithalf, questiontype, inclusive) %>%
  filter(splithalf == 1, questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))


exp2_sh1_prep <- dat %>%
  filter(term == 'su_21' | term == 'fa_21') %>%
  select(experimenter, splithalf, questiontype, inclusive) %>%
  filter(splithalf == 1, questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

exp2_sh2_noprep <- dat %>%
  filter(term == 'su_21' | term == 'fa_21') %>%
  select(experimenter, splithalf, questiontype, inclusive) %>%
  filter(splithalf == 2, questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))


exp2_sh2_prep <- dat %>%
  filter(term == 'su_21' | term == 'fa_21') %>%
  select(experimenter, questiontype, inclusive, splithalf) %>%
  filter(splithalf == 2, questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))


exp2_sh1_difference <- exp2_sh1_prep$meanresponse - exp2_sh1_noprep$meanresponse

exp2_sh2_difference <- exp2_sh2_prep$meanresponse - exp2_sh2_noprep$meanresponse


cor.test(exp2_sh1_difference, exp2_sh2_difference)
```


#### ICC for Splithalf - Experiment 2
```{r}
#make the two priming effects kith
exp2_prime_sh1 <- as.data.frame(exp2_sh1_difference)
exp2_prime_sh2 <- as.data.frame(exp2_sh2_difference)

exp2_primes_sh <- cbind(exp1_prime_sh1, exp1_prime_sh2)

icc(exp2_primes_sh, model = "twoway", type = "agreement", unit = "single")
```


#### Test-Retest - Experiment 2
```{r}
exp2_round1_reliability_noprep <- dat %>%
  filter(round == 1 & term == "su_21" | round == 1 & term == "fa_21") %>%
  select(experimenter, round, questiontype, inclusive, term) %>%
  filter(questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

exp2_round1_reliability_prep <- dat %>%
  filter(round == 1 & term == "su_21" | round == 1 & term == "fa_21") %>%
  select(experimenter, round, questiontype, inclusive, term) %>%
  filter(questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))

exp2_round2_reliability_noprep <- dat %>%
  filter(round == 2 & term == "su_21" | round == 2 & term == "fa_21") %>%
  select(experimenter, round, questiontype, inclusive, term) %>%
  filter(questiontype == 'noprep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))


exp2_round2_reliability_prep <- dat %>%
  filter(round == 2 & term == "su_21" | round == 2 & term == "fa_21") %>%
  select(experimenter, round, questiontype, inclusive, term) %>%
  filter(questiontype == 'prep') %>%
  group_by(experimenter) %>%
  summarise(meanresponse = mean(inclusive, na.rm = TRUE))


exp2_round1_difference <- exp2_round1_reliability_prep$meanresponse - exp2_round1_reliability_noprep$meanresponse

exp2_round2_difference <- exp2_round2_reliability_prep$meanresponse - exp2_round2_reliability_noprep$meanresponse

cor.test(exp2_round1_difference, exp2_round2_difference)
```


#### ICC for Test-Retest - Experiment 2
```{r}
#make the two priming effects kith
exp2_prime_sh1 <- as.data.frame(exp2_round1_difference)
exp2_prime_sh2 <- as.data.frame(exp2_round2_difference)

exp2_primes <- cbind(exp2_prime_sh1, exp2_prime_sh2)

icc(exp2_primes, model = "twoway", type = "agreement", unit = "single")
```


## Exploratory {.tabset}

### Path Model
```{r}
modelIM = '
answer~conventional+direct+rating+dollarsigns+questiontype

full~conventional+direct+answer+rating+dollarsigns+questiontype

IM~full+conventional+direct+answer+rating+dollarsigns+questiontype'

fitIM <- sem(model = modelIM, data = dat)
summary(fitIM)

```

```{r}
labels <- list(questiontype = "Question Type", conventional = "Conventional", direct = "Direct", dollarsigns = "Dollar Signs", rating = "Rating", answer = "Answer", full = "Full Sentence", IM = "Prep Match")

#lavaanPlot(model = fitIM, labels = labels,
           #node_options = list(shape = "box", 
                               #fontname = "Helvetica"), 
           #edge_options = list(color = "grey"), 
           #coefs = FALSE)

lavaanPlot(model = fitIM, labels = labels,
           node_options = list(shape = "box", 
                               fontname = "Helvetica"), 
           edge_options = list(color = "grey"), 
           coefs = FALSE, sig = .05, stars="regress")

```

